Predicting the effects of character displacement on food-web dynamics

### 2019-03-22 supplementary_ECD_model.Rmd
added final edits and sent to Seth, JP, and Matt Osmond for friendly reviews.

---
#title: |
#   | Predicting the effects of character displacement on food-web dynamics
#   | Food-web dynamics under ecological character displacement
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$
# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib 
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

\vspace*{0.1cm} 
\begin{center} \LARGE Appendix S**?**: \\ Ecological character displacement destabilizes food webs \end{center}
<!--\begin{center} \LARGE Food-web dynamics under ecological character displacement \end{center}-->

@@

*Elements*: Figure S1 and figure S2.

<!-- End title page formatting -->

\linenumbers{}
\modulolinenumbers[3]

@@

.

```{r McCann_Plot, echo=FALSE, fig.pos="H", fig.cap="**Effect of character displacement when consumers exhibit a more realistic functional response.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panel). This figure illustrates how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource abundances and concomitant decrease in food-web stability. Initial parameter and state variables are given in the main text."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

Figure 2: **Robustness to consumer asymmetry**. Scenarios correspond to: (I) resources occur in the same habitat and consumer(s) exhibits a linear functional response; (II) resources occur in different habitats and consumer(s) exhibits a linear functional response; (III) resources occur in different habitats and consumer(s) exhibits a more realistic functional response (details in main text). Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panels). The similarity between this figure and fig. S1 and fig. 2 (main text) show that adding an asymmetry in consumer attack rates does not alter the conclusions reported in the main text. If anything, it is more likely an asymmetry will push the system toward the boundary of stability (note position of large circles in stability panel of Scenario I). Details of the consumer asymmetry simulation are given in the main text.

>>>>

---
#title: |
#   | Predicting the effects of character displacement on food-web dynamics
#   | Food-web dynamics under ecological character displacement
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$
# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib 
#    includes:  
#      in_header: Am-Nat-preamble-latex.tex
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{fullpage}
- \linespread{1.7}
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

\vspace*{0.1cm} 
\begin{center} \LARGE Appendix S4: \\ Ecological character displacement destabilizes food webs \end{center}
<!--\begin{center} \LARGE Food-web dynamics under ecological character displacement \end{center}-->

@@

*Elements*: Figures S1 and S2.

<!-- End title page formatting

\linenumbers{}
\modulolinenumbers[3]
-->

@@

(ignore this blank page for the moment. Rmarkdown can be a pain in the ass.)

```{r McCann_Plot, echo=FALSE, fig.pos="H", fig.cap="Figure S1: **Effect of character displacement when consumers exhibit a more realistic functional response.** Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panel). This figure illustrates how, regardless of the tradeoff, character displacement increases the effective attack rate of consumers. This always resulted in a suppression of resource abundances and concomitant decrease in food-web stability. Initial parameter and state variables are given in the main text."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

Figure S2: **Robustness to consumer asymmetry**. Scenarios correspond to: (I) resources occur in the same habitat and consumer(s) exhibits a linear functional response; (II) resources occur in different habitats and consumer(s) exhibits a linear functional response; (III) resources occur in different habitats and consumer(s) exhibits a more realistic functional response (details in main text). Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in stability panels). The similarity with fig. S1 and fig. 2 (main text) show that adding an asymmetry in consumer attack rates does not alter the conclusions reported in the main text. If anything, it is more likely that an asymmetry will push the system toward the boundary of stability (note position of large circles in stability panel of Scenario I). Details of the consumer asymmetry simulation are given in the main text.
